Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-06-06 supplement/06_bat_data.Rmd
correct recurse code inline function

```{r summarise_counts}
data_heatmap = copy(data)
data_heatmap[, c("xround", "yround") := list(
  plyr::round_any(X, 250),
  plyr::round_any(Y, 250)
)]
data_heatmap = data_heatmap[, .N, by = c("xround", "yround")]
```

```{r plot_heatmap}
fig_heatmap = 
ggplot(data_heatmap)+
  geom_tile(
    aes(
      xround, yround, fill = N
    ),
    colour = "grey",
    size = 0.1,
    show.legend = F
  )+
  scale_fill_viridis_c(
    option = "C",
    direction = 1,
    trans = "log10"
  )+
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(crs = 2039)

@@

```{r sampling_interval_check, echo=FALSE}
# get intervals per individual
data_for_intervals = data[,list(lags = list(diff(TIME/1000))), by = "TAG"]
data_for_intervals = data_for_intervals[,list(lag = unlist(lags, recursive = F)), by = "TAG"]

# make figure
fig_lags = 
ggplot(data_for_intervals)+
  geom_histogram(
    aes(
      x = lag / 8,
      fill = (lag / 8 > 3)
    ),
    position = position_identity(),
    bins = 15,
    # fill = "grey",
    col = "black",
    show.legend = F
  )+
  geom_vline(
    xintercept = 1,
    col = "red"
  )+
  scale_x_log10(
    labels = function(x) {sprintf("%ix", x)},
    breaks = c(1, 3, 10, 100, 1000)
  )+
  scale_y_sqrt()+
  scale_fill_viridis_d(
    option = "H",
    begin = 0.1,
    end = 0.8
  )+
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  )+
  labs(x = "Sampling interval")

@@

```{r localisation_error, echo=FALSE}
fig_error_histogram = 
ggplot(data)+
  geom_histogram(
    aes(
      x = sqrt(VARX),
      fill = (sqrt(VARX) > 100)
    ),
    bins = 15,
    # fill = "grey",
    col = "black",
    show.legend = F
  )+
  scale_fill_viridis_d(
    option = "H",
    begin = 0.1,
    end = 0.8
  )+
  scale_x_log10(
    labels = function(x) {sprintf("%2.fm", x)}
  )+
  scale_y_sqrt()+
  coord_cartesian(
    xlim = c(0.5, 5e3)
  )+
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  )+
  labs(x = "Variance X")

@@

```{r echo=FALSE}

```

@@

```{r plot_focus_bad_speed}
# this figure for the panel in main text figure 1
fig_bat_focus_bad_speed = 
  fig_bat_raw +
  coord_sf(
    crs = 2039,
    xlim = c(253000, NA),
    ylim = c(772000, NA)
  )

@@

```{r}
# get residence times

data_residence <- lapply(data_smooth, function(dt) {
  # do basic recurse
  dt_recurse <- getRecursions(
    x = dt[, c("X", "Y", "time", "TAG")],
    radius = 50,
    timeunits = "mins"
  )

@@

  # print message when done
  message(sprintf("TAG %i residence times done", unique(dt$TAG)))
})
```

>>>>

```{r summarise_counts}
data_heatmap <- copy(data)
data_heatmap[, c("xround", "yround") := list(
  plyr::round_any(X, 250),
  plyr::round_any(Y, 250)
)]
data_heatmap <- data_heatmap[, .N, by = c("xround", "yround")]
```

```{r plot_heatmap}
fig_heatmap <-
  ggplot(data_heatmap) +
  geom_tile(
    aes(
      xround, yround,
      fill = N
    ),
    colour = "grey",
    size = 0.1,
    show.legend = F
  ) +
  scale_fill_viridis_c(
    option = "C",
    direction = 1,
    trans = "log10"
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  ) +
  coord_sf(crs = 2039)

@@

```{r sampling_interval_check, echo=FALSE}
# get intervals per individual
data_for_intervals <- data[, list(lags = list(diff(TIME / 1000))), by = "TAG"]
data_for_intervals <- data_for_intervals[, list(lag = unlist(lags, recursive = F)), by = "TAG"]

# make figure
fig_lags <-
  ggplot(data_for_intervals) +
  geom_histogram(
    aes(
      x = lag / 8,
      fill = (lag / 8 > 3)
    ),
    position = position_identity(),
    bins = 15,
    # fill = "grey",
    col = "black",
    show.legend = F
  ) +
  geom_vline(
    xintercept = 1,
    col = "red"
  ) +
  scale_x_log10(
    labels = function(x) {
      sprintf("%ix", x)
    },
    breaks = c(1, 3, 10, 100, 1000)
  ) +
  scale_y_sqrt() +
  scale_fill_viridis_d(
    option = "H",
    begin = 0.1,
    end = 0.8
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  ) +
  labs(x = "Sampling interval")

@@

```{r localisation_error, echo=FALSE}
fig_error_histogram <-
  ggplot(data) +
  geom_histogram(
    aes(
      x = sqrt(VARX),
      fill = (sqrt(VARX) > 100)
    ),
    bins = 15,
    # fill = "grey",
    col = "black",
    show.legend = F
  ) +
  scale_fill_viridis_d(
    option = "H",
    begin = 0.1,
    end = 0.8
  ) +
  scale_x_log10(
    labels = function(x) {
      sprintf("%2.fm", x)
    }
  ) +
  scale_y_sqrt() +
  coord_cartesian(
    xlim = c(0.5, 5e3)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank(),
    axis.text.x = element_text(
      face = "bold",
      size = 16
    ),
    axis.title.y = element_blank(),
    axis.title.x = element_text(
      face = "bold",
      size = 16
    )
  ) +
  labs(x = "Variance X")

@@

@@

```{r plot_focus_bad_speed}
# this figure for the panel in main text figure 1
fig_bat_focus_bad_speed <-
  fig_bat_raw +
  coord_sf(
    crs = 2039,
    xlim = c(253000, NA),
    ylim = c(772000, NA)
  )

@@

```{r}
# get residence times
data_residence <- lapply(data_smooth, function(dt) {
  # do basic recurse
  dt_recurse <- getRecursions(
    x = dt[, c("X", "Y", "time", "TAG")],
    radius = 50,
    timeunits = "mins"
  )

@@

  # print message when done
  message(sprintf("TAG %s residence times done", unique(dt$TAG)))

  dt
})
```
